\documentclass[10pt,letterpaper,titlepage]{article}
\usepackage{titletoc}

\usepackage{ifthen,varioref}
\usepackage{url}
\usepackage{titlesec}
\usepackage{fullpage}
\usepackage{hyperref}

% fix block paragraphs in toc
\usepackage{parskip}
% use block paragraphs
\setlength{\parindent}{0pt}
%\setlength{\parskip}{\baselineskip}
\setlength{\parskip}{4pt}

\newcommand\corpname{Gainesville Hackerspace, Inc.}
\newcommand\approvaldate{March 9, 2010}

\hypersetup{
    pdfauthor={Ian Taylor},
    pdftitle={\corpname{} Policies},
    pdfborder={0 0 0},
    pdfsubject={policies},
    pdfkeywords={policies, \corpname},
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue,
    bookmarks=true,
    colorlinks=false
}

\titlecontents{section}[1.5em]
    {}
    {\contentslabel{2.0em}}
    {\hspace*{-2.0em}}
    {\titlerule*[1pc]{.}\contentspage}

\renewcommand\thesection{\Roman{section}}
\renewcommand\thesubsection{\arabic{subsection}}
\titleformat{\section}{\bfseries\Large}{Article~\thesection}{0.5em}{}
\titleformat{\subsection}{\bfseries\large}{Section~\thesubsection}{0.5em}{}
\labelformat{section}{Article~#1}
\labelformat{subsection}{\protect\iscurrentsection{\thesection}Section~#1}
\newcommand\iscurrentsection[1]{%
    \ifthenelse{\equal{#1}{\thesection}}{}{Article~#1~}}

% for things like 1\st 2\nd 3\rd 4\th
\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
\renewcommand{\th}[0]{\superscript{th}}
\newcommand{\st}[0]{\superscript{st}}
\newcommand{\nd}[0]{\superscript{nd}}
\newcommand{\rd}[0]{\superscript{rd}}

\title{%
    \textsc{\LARGE \corpname \\
    \Large Policies
    }
}
\date{\today}
\author{}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Membership Dues}
\label{dues}

Dues are due before the 01\st{} of the month. Each month's membership is
prepaid. If payment has not been received by the start of a month membership
is suspended and the member's 24/7 access will be disabled. (Nevertheless, a
suspended member may still visit as a guest as below in \ref{guests}.

Any suspended member may be brought current and immediately reinstated upon
payment for the current month.

Instead of immediate reinstatement, a suspended member may designate payment to
be applied to the following month, in which case the suspension will be lifted
at the start of that following month.

Newly voted membership is effective upon payment for the current month.

As a courtesy, an invoice for each month will be emailed about the 15\th{}
of each month, and a reminder about a week later.

Dues may not be waived. Dues paid mid-month are not prorated.

\section{Meeting Schedule}

Open meetings will be held weekly, on Tuesday evening, starting at 7:00 PM.

Board meetings will be held the first Tuesday of the month, adjacent
to or during the weekly open meeting.

Membership meetings will be held the first Tuesday of the month,
adjacent to or during the weekly open meeting.

\section{Guests}
\label{guests}
Guests are welcome on the premises so long as they are accompanied by a sponsor
member. The sponsor member is responsible for the guest while they are on
premises.

\end{document}
